Isabelle/C/AutoCorres - A Show-Case for a Semantic Back-End for Isabelle/C

### 2019-10-30 C11-BackEnds/AutoCorres_wrapper/document/root.tex
build

\newenvironment{matharray}[1]{\[\begin{array}{#1}}{\end{array}\]} % from 'iman.sty'
\newcommand{\indexdef}[3]%
{\ifthenelse{\equal{}{#1}}{\index{#3 (#2)|bold}}{\index{#3 (#1\ #2)|bold}}} % from 'isar.sty'
\newcommand{\isactrlC}{{\isacommand C}}
\newcommand{\isactrlmkUNDERSCOREstring}{\isakeywordcontrol{mk{\isacharunderscore}string}}
\newcommand{\isactrlMLPRIME}{{\isacommand ML{\isacharprime}}}

@@

\title{Isabelle/C/Clean - A Show-Case for a Semantic Back-End for Isabelle/C}
\author{%
  \href{https://www.lri.fr/~ftuong/}{Fr\'ed\'eric Tuong}
  \and
  \href{https://www.lri.fr/~wolff/}{Burkhart Wolff}}
\publishers{%
  \mbox{LRI, Univ. Paris-Sud, CNRS, Universit\'e Paris-Saclay} \\
  b\^at. 650 Ada Lovelace, 91405 Orsay, France \texorpdfstring{\\}{}
}

@@

Clean is such a semantic back-end, i.e. an Isabelle theory providing a
semantics and execution model. Clean is an abstract, ``shallow-style
embedding'' for an imperative core language. It strives for a type-safe
notation of program-variables, an incremental construction of the typed
state-space, support of incremental verification, and open-world extensibility
of new type definitions being intertwined with the program definitions.

Clean is based on a ``no-frills'' state-exception monad with the usual
definitions of \isa{bind} and \isa{unit} for the compositional glue of
state-based computations.  Clean offers conditionals and loops supporting
C-like control-flow operators such as \isa{break} and \isa{return}. The
state-space construction is based on the extensible record package. Direct
recursion of C-functions is supported.

The current session instantiates Isabelle/C with Clean and produces the
Isabelle/C/Clean instance. It is conceived as a demonstrator for creating other
instances of Isabelle/C with other semantic backends such as
AutoCorres~\cite{DBLP:conf/pldi/GreenawayLAK14},
IMP2~\cite{DBLP:journals/afp/LammichW19} or Orca~\cite{bockenek:hal-02069705}.
\end{abstract}

@@

\inputif{1/document/Clean_Wrapper.tex}

\inputif{2/document/Prime.tex}
\inputif{2/document/IsPrime_sqrt_outside.tex}
\inputif{2/document/Quicksort.tex}
\inputif{2/document/Quicksort2.tex}

\inputif{1/document/Init.tex}
\inputif{1/document/Meta_C.tex}
\inputif{1/document/Core.tex}
\chapter{Appendix: Miscellaneous (Interface to ``typedecl'')}
\inputif{1/document/Isabelle_code_runtime.tex}
\chapter{Appendix: Miscellaneous (Overloading ``code\_reflect'')}
\inputif{1/document/Isabelle_typedecl.tex}
\inputif{1/document/Generator_dynamic_sequential.tex}
\inputif{2/document/Clean_backend_old.tex}

>>>>

\newenvironment{matharray}[1]{\[\begin{array}{#1}}{\end{array}\]} % from 'iman.sty'
\newcommand{\indexdef}[3]%
{\ifthenelse{\equal{}{#1}}{\index{#3 (#2)|bold}}{\index{#3 (#1\ #2)|bold}}} % from 'isar.sty'
\newcommand{\isactrlC}{{\isacommand C}}

@@

\title{Isabelle/C/AutoCorres - A Show-Case for a Semantic Back-End for Isabelle/C}
\author{%
  \href{https://www.lri.fr/~ftuong/}{Fr\'ed\'eric Tuong}
  \and
  \href{https://www.lri.fr/~wolff/}{Burkhart Wolff}}
\publishers{%
  \mbox{LRI, Univ. Paris-Sud, CNRS, Universit\'e Paris-Saclay} \\
  b\^at. 650 Ada Lovelace, 91405 Orsay, France \texorpdfstring{\\}{}
}

@@

The current session instantiates Isabelle/C with AutoCorres and produces the
Isabelle/C/AutoCorres instance. It is conceived as a demonstrator for creating other
instances of Isabelle/C with other semantic backends such as
Clean~\cite{journals/afp/TuongW19},
IMP2~\cite{DBLP:journals/afp/LammichW19} or Orca~\cite{bockenek:hal-02069705}.
\end{abstract}

@@

\inputif{1/document/README.tex}
\inputif{1/document/AutoCorres_Wrapper.tex}

\inputif{2/document/IsPrime_integrated.tex}
\inputif{2/document/IsPrime_linear_outside.tex}
\inputif{2/document/IsPrime_sqrt_outside.tex}
\inputif{2/document/IsPrime_sqrt_opt_outside.tex}
\inputif{2/document/Parse_for_loop.tex}
\inputif{2/document/Quicksort.tex}
\inputif{2/document/TestSEL4.tex}
